The problem and promise of scale in multilayer animal social networks

### 2020-05-27 paper/manuscript-rev.Rmd
fst rev

Our examinations is motivated by behavioural, landscape, and spatial ecology to
build a conceptual and analytical framework for scale-dependent multilayer
networks, and we apply this framework to a case study of caribou (*Rangifer
tarandus*) in Newfoundland, Canada [@Peignier_2019]. We use this case study to
address two principal questions associated with scale-dependent multilayer
networks. First, to what degree does the social scale of relationships, spatial
scale of landscapes, and temporal scale of analysis influence our ability to
interpret complex social systems? Second, can variation in the social, spatial,
and temporal scale improve predictions associated with biological differences in
seasonal resource availability and social association? We conclude with
perspectives for further development and application of scale in multilayer
networks with respect to phenotypes and individual fitness,
movement ecology and collective movement, and habitat selection
and space use.
<!-- TODO: we answer the first question in the discussion, but not the second-->
<!-- TODO: Webber reference should be 2018, but defaulting to 2017-->

(ref:spacetime) Space-time diagram representing variation the relative spatial and temporal extent required for different types of social and communication processes for four species, including spotted hyaena, passerine birds, sleepy lizards, and elephants. Spatial and temporal extent for social interactions, e.g. mating, grooming, or aggression, are similar for most species because physical contact between two individuals is required for many social interactions. The logical extension is that spatial and temporal extent for social interaction is hierarchically nested within the spatial and temporal extent for social association because individuals must share space to interact. By contrast, different species have potential for greater spatial and temporal extents, for example, temporal extent for vocal communication is similar for most species because most vocal calls only persist in the environment for seconds, but spatial extent for vocal communication is highly variable with elephant calls extending the great distance and passerine calls extending the shortest distance.

<!-- TODO: units of spatial scale? --> 
<!-- TODO: citations? -->

# Scale in multilayer networks: a case study

@@

# Perspectives to advance multilayer networks

The integration of behavioural and ecological theory has shown the value of
considering the importance of various ecological disciplines to better
understand and predict animal social networks, including demography
[@Shizuka_2019], evolutionary and quantitative genetics [@Fisher_2017], disease
ecology [@Silk_2017], and animal personality [@Sih_2018]. While the number of
studies integrating social network theory into a broader array of behavioural
and ecological sub-disciplines is impressive, only recently has the role of
animal space use been considered in describing the causes and consequences of
the social environment in the context of (1) phenotypes and individual fitness
[@Webber_2018], (2) movement ecology and collective movement [@Bode_2011], and
(3) habitat selection and space use [@He_2019]. Importantly, much of the work
linking space use and the social environment has been theoretical and empirical
studies are lacking [but see @Peignier_2019; @Strandburg_Peshkin_2015;
@Strandburg_Peshkin_2017]. Here, we discuss the role of scale and multilayer
networks in the emerging integration of social and spatial ecology within the
behavioural ecology literature.

## Phenotypes and Individual fitness

## Movement ecology and collective movement

## Habitat selection and space use
Social structure and habitat selection are intimately linked: individuals must
share space to interact and the distribution of resources influences group
dynamics and home range size [@Webber_2018]. Social structure is influenced by
resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
and fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
is a scale-dependent process [@Mayor_2009]. Multilayer networks represent a
novel framework for considering the influence of habitat selection and space use
on sociality across scales.

>>>>

Our examinations is motivated by behavioural, landscape, and spatial ecology to
build a conceptual and analytical framework for scale-dependent multilayer
networks, and we apply this framework to a case study of caribou (*Rangifer
tarandus*) in Newfoundland, Canada [@Peignier_2019]. We use this case study to
address two principal questions associated with scale-dependent multilayer
networks. First, to what degree does the social scale of relationships, spatial
scale of landscapes, and temporal scale of analysis influence our ability to
interpret complex social systems? Second, can variation in the social, spatial,
and temporal scale improve predictions associated with biological differences in
seasonal resource availability and social association? We conclude with
perspectives for further development and application of scale in multilayer
networks with respect to phenotypes and individual fitness,
movement ecology and collective movement, and habitat selection
and space use.

<!-- # Perspectives to advance multilayer networks  -->

<!-- The integration of behavioural and ecological theory has shown the value of -->
<!-- considering the importance of various ecological disciplines to better -->
<!-- understand and predict animal social networks, including demography -->
<!-- [@Shizuka_2019], evolutionary and quantitative genetics [@Fisher_2017], disease -->
<!-- ecology [@Silk_2017], and animal personality [@Sih_2018]. While the number of -->
<!-- studies integrating social network theory into a broader array of behavioural -->
<!-- and ecological sub-disciplines is impressive, only recently has the role of -->
<!-- animal space use been considered in describing the causes and consequences of -->
<!-- the social environment in the context of (1) phenotypes and individual fitness -->
<!-- [@Webber_2018], (2) movement ecology and collective movement [@Bode_2011], and -->
<!-- (3) habitat selection and space use [@He_2019]. Importantly, much of the work -->
<!-- linking space use and the social environment has been theoretical and empirical -->
<!-- studies are lacking [but see @Peignier_2019; @Strandburg_Peshkin_2015; -->
<!-- @Strandburg_Peshkin_2017]. Here, we discuss the role of scale and multilayer -->
<!-- networks in the emerging integration of social and spatial ecology within the -->
<!-- behavioural ecology literature. -->

# Phenotypes and Individual fitness

# Movement ecology and collective movement

# Habitat selection and space use
Social structure and habitat selection are intimately linked: individuals must
share space to interact and the distribution of resources influences group
dynamics and home range size [@Webber_2018]. Social structure is influenced by
resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
and fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
is a scale-dependent process [@Mayor_2009]. Multilayer networks represent a
novel framework for considering the influence of habitat selection and space use
on sociality across scales.

---
# Scale in multilayer networks: a case study

@@

---
